---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jamestools

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![CRAN status](https://www.r-pkg.org/badges/version/jamestools)](https://CRAN.R-project.org/package=jamestools)
[![Codecov test coverage](https://codecov.io/gh/JamesHWade/jamestools/branch/master/graph/badge.svg)](https://app.codecov.io/gh/JamesHWade/jamestools?branch=master)
[![R-CMD-check](https://github.com/JamesHWade/jamestools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JamesHWade/jamestools/actions/workflows/R-CMD-check.yaml)
[![pre-commit](https://img.shields.io/badge/pre--commit-enabled-brightgreen?logo=pre-commit)](https://github.com/pre-commit/pre-commit)
![Activity](https://img.shields.io/github/last-commit/jameshwade/jamestools)
<!-- badges: end -->

The goal of jamestools is to be a set of convenience functions to my personal development work. I double these are of interest to most, but it's a convenient place to play with package building tools without breaking something others want to use.

## Installation

You can install the development version of jamestools like so:

``` r
require(remotes)
remotes::install_github("JamesHWade/jamestools")
```

## Search

Ag - the Silver Searcher is a convenient search function I use all the time in the terminal. `ag()` gives you a function to call that in the R console.

```{r example}
library(jamestools)
ag("dplyr", filetype = "R")
```
